---
title: "iteration_and_listcols"
author: "Jiayi Shen"
date: "10/30/2018"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
set.seed(1)
```

##Vectors
```{r, error = TRUE}

vec_numeric = 5:8
vec_char = c("My", "name", "is", "Jeff")
vec_logical = c(TRUE, TRUE, TRUE, FALSE)

# Trying to join the following vectors will result in coersion
vec_numeric + vec_logical
vec_char + vec_numeric
vec_numeric + vec_numeric
```

A column in df can be a list of lists. make sure that the column has the same length as other entries.


```{r}
l = list(vec_numeric = 5:8,
         mat         = matrix(1:8, 2, 4),
         vec_logical = c(TRUE, FALSE),
         summary     = summary(rnorm(1000)))

# is l a alist?
is.list(l)

#call the second element of list
l[[2]]
```



```{r}
df = data_frame(
  a = rnorm(20, 3, 1),
  b = rnorm(20, 0, 5),
  c = rnorm(20, 10, .2),
  d = rnorm(20, -3, 1)
)



mean_and_sd = function(x) {
  
  if (!is.numeric(x)) {
    stop("Argument x should be numeric")
  } else if (length(x) == 1) {
    stop("Cannot be computed for length 1 vectors")
  }
  
  mean_x = mean(x)
  sd_x = sd(x)

  tibble(
    mean = mean_x, 
    sd = sd_x
  )
}

```

We can apply the function to `df`

```{r}
# apply mean_and_sd function to the first element of the df. 
mean_and_sd(df[[1]])
```

##for loop
- input object
- output object

```{r}
# better to specify an empty output list ahead of time.
output = vector(mode = "list", length = 4)

#use a for loop to iterate.
for (i in 1:4) {
  output[[i]] = mean_and_sd(df[[i]])
}
```


## map
lets replace the for loop with map to accomplish the exact same output. 

```{r}
output = map(df, mean_and_sd)

#map statement embed pretty well to tidyverse. 
df %>% 
  select(a,b) %>% 
  map(mean_and_sd)
```

try a different function 
```{r}
output = map(df, summary)
```

## map variants 

if you know what your outputs type will be...
```{r}
map(df, median)
map_dbl(df, median)

```


## code syntax
be clear about arguments!

```{r}
# produce the exact same result as the above.  
map(.x = df, ~ mean_and_sd(x = .x))
```


## inclass exercise
```{r}

library(rvest)
read_page_reviews <- function(url) {
  
  h = read_html(url)
  
  title = h %>%
    html_nodes("#cm_cr-review_list .review-title") %>%
    html_text()
  
  stars = h %>%
    html_nodes("#cm_cr-review_list .review-rating") %>%
    html_text() %>%
    str_extract("\\d") %>%
    as.numeric()
  
  text = h %>%
    html_nodes(".review-data:nth-child(4)") %>%
    html_text()
  
  data_frame(title, stars, text)
}

url_base = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber="
vec_urls = str_c(url_base, 1:5)


reviews = vector(mode = "list", length = 5)
for (i in 1:5) {
  reviews[[i]] = read_page_reviews(vec_urls[[i]])
}

```


```{r}
# Alternatively we can use map_df 
map_df(vec_urls, read_page_reviews)
```


## nesting
```{r}
library(rnoaa)

weather = 
  meteo_pull_monitors(c("USW00094728", "USC00519397", "USS0023B17S"),
                      var = c("PRCP", "TMIN", "TMAX"), 
                      date_min = "2016-01-01",
                      date_max = "2016-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY", 
                      USC00519397 = "Waikiki_HA",
                      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

```{r}
# Weather data will be separated into three station-specific data frames
# each of which is the data “observation” for the respective station.

weather_nest = 
  nest(weather, date:tmin)

#alternativly, we can group by and then nest.
weather %>% 
  group_by(name, id) %>% 
  nest()
```

## unnesting

```{r}
weather_nest %>% unnest()
```

## List column elements
```{r}
weather_nest$data[[1]] %>% 
  skimr::skim()
```


Fit a location-specific regression ...
```{r}
lm(tmax~tmin, data = weather_nest$data[[1]] )
lm(tmax~tmin, data = weather_nest$data[[2]] )
lm(tmax~tmin, data = weather_nest$data[[3]] )

```

write a function!!
```{r}
weather_lm = function(df) {
  lm(tmax~tmin, data = df)
}

# use weather_lm as the input of a separate function
map (.x = weather_nest$data, ~  weather_lm)
```

save output as a new list column ..
```{r}
weather_nest %>% 
  mutate (lm_result = map (.x = data, ~  weather_lm))
```


```{r}

```

