---
title: "Writing_functions"
author: "Jiayi Shen"
date: "10/25/2018"
output: html_document
---

```{r setup}
library(tidyverse)
set.seed(1)

```

my first function
```{r}
x = rnorm(25, mean = 5, sd = 3)

# standardization 
(x - mean(x)) / sd(x)
```


write a function to compute z scores for a vector. 

```{r}
z_scores = function (x) {
  
  (x - mean(x)) / sd(x)
  
}
```


check to see if this works ... 

```{r}
uniform_sample = runif(100)

z_scores(uniform_sample)
```

check some other examples ...
```{r, error = TRUE}
z_scores(3)

z_scores("my name is jeff")

z_scores(iris)

z_scores(sample(c(TRUE, FALSE), 25, replace = TRUE))
```


put in some checks on inputs ... 
recommend to do 

```{r, error = TRUE}
z_scores = function(x) {
  
  if (!is.numeric(x)) {
    stop("Argument x should be numeric")
  } else if (length(x) == 1) {
    stop("Z scores cannot be computed for length 1 vectors")
  }
  
  z = mean(x) / sd(x)
  
  z
}

z_scores(3)
z_scores("my name is jeff")
```



just output mean and sd....
put multiple outputs in a tibble (remember to load tidyverse library)

```{r}
mean_and_sd = function(x) {
  
  if (!is.numeric(x)) {
    stop("Argument x should be numeric")
  } else if (length(x) == 1) {
    stop("Z scores cannot be computed for length 1 vectors")
  }
  
  tibble (
    mean(x),
    sd(x)
  )

}

mean_and_sd(x)
```


multiple inputs...

looking at simple linear regression;  

```{r}
sim_data = tibble(
  x = rnorm(30, mean = 1, sd = 1),
  y = 2 + 3 * x + rnorm(30, 0, 1)
)

ls_fit = lm(y ~ x, data = sim_data)
  
beta0_hat = coef(ls_fit)[1]
beta1_hat = coef(ls_fit)[2]
```

Now make everything into a function
inputs are sample size and coefficients.

```{r}
sim_regression = function(n, beta0 = 2, beta1 = 3) {
  #here assigned default values to beta0 and beta1
  
  sim_data = tibble(
    x = rnorm(n, mean = 1, sd = 1),
    y = beta0 + beta1 * x + rnorm(n, 0, 1)
  )
  
  ls_fit = lm(y ~ x, data = sim_data)
  
  tibble(
    beta0_hat = coef(ls_fit)[1],
    beta1_hat = coef(ls_fit)[2]
  )
}

sim_regression(100, beta0 = 4, beta1 = 4)
#order of the arguments does not matter. 
sim_regression(beta0 = 4,100, beta1 = 4)
#the following works but not recommended. 
sim_regression(100, 4, 4)
```


```{r}
library(rvest)
url = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=1"

dynamite_html = read_html(url)

review_titles = dynamite_html %>%
  html_nodes("#cm_cr-review_list .review-title") %>%
  html_text()

review_stars = dynamite_html %>%
  html_nodes("#cm_cr-review_list .review-rating") %>%
  html_text()

review_text = dynamite_html %>%
    html_nodes(".review-data:nth-child(4)") %>%
    html_text()

reviews = tibble(
  title = review_titles,
  stars = review_stars,
  text = review_text
)
```


```{r}
read_page_reviews <- function(url) {
  
  h = read_html(url)
  
  title = h %>%
    html_nodes("#cm_cr-review_list .review-title") %>%
    html_text()
  
  stars = h %>%
    html_nodes("#cm_cr-review_list .review-rating") %>%
    html_text() %>%
    str_extract("\\d") %>%
    as.numeric()
  
  text = h %>%
    html_nodes(".review-data:nth-child(4)") %>%
    html_text()
  
  data_frame(title, stars, text)
}

#execute
read_page_reviews (url)
```


```{r}
extract_data = function (cell_range, movie_title){
  df = readxl::read_excel("./data/LotR_Words.xlsx", range = cell_range) %>% 
    janitor::clean_names() %>%
    gather(key = sex, value = words, female:male) %>%
    mutate(race = tolower(race)) 
  df
}

extract_data(, cell_range = "B3:D6")
```


```{r}
f = function(x) {
  z = x + y #search the global environment for any values of "y"
  z
}

x = 1
y = 2

f(x = y)
```

